### 2015-11-20 preliminaries.tex
Few improvements

\textbf{Convex Analysis.} The \emph{Bregman divergence} of a convex
differentiable function $f$ is defined as $\Breg_f(u,v) = f(u) - f(v) - \langle
\grad f(v), u - v \rangle$.  Note that $\Breg_f(u,v) \ge 0$ for any $u,v$ which
follows directly from the definition of convexity of $f$.

The \emph{Fenchel conjugate} of a function $f:K \to \R$ is the function
$f^*:V^* \to \R \cup \{+\infty\}$ defined as $f^*(\ell) = \sup_{w \in K} \left(
\langle \ell, w \rangle - f(w) \right)$.  The Fenchel conjugate of any function
is convex (since it is a supremum of affine functions) and satisfies for all $w
\in K$ and all $\ell \in V^*$  the \emph{Fenchel-Young inequality}
$
f(w) + f^*(\ell) \ge \langle \ell, w \rangle
$.

@@

\begin{proposition}[Fenchel Conjugates of Strongly Convex Functions]
\label{proposition:conjugate-properties}
Let $K \subseteq V$ be a non-empty closed convex set with diameter $D:=\sup_{u,v \in K} \|u-v\|$.
Let $\lambda > 0$, and let $f:K \to \R$ be a lower semi-continuous function
that is $\lambda$-strongly convex with respect to $\|\cdot\|$.
The Fenchel conjugate of $f$ satisfies:
\begin{enumerate}
\item $f^*$ is finite everywhere and differentiable.
\item $\grad f^*(\ell) = \argmin_{w \in K} \left( f(w) - \langle \ell, w \rangle \right)$
\item For any $\ell \in V^*$,
$f^*(\ell) + f(\grad f^*(\ell)) = \langle \ell, \grad f^*(\ell) \rangle$.
\item $f^*$ is $\frac{1}{\lambda}$-strongly smooth i.e. for any $x,y \in V^*$,
$\Breg_{f^*}(x, y) \le \frac{1}{2\lambda} \|x - y\|_*^2$.

\item $f^*$ has $\frac{1}{\lambda}$-Lipschitz continuous gradients i.e.
$\|\grad f^*(x) - \grad f^*(y)\| \le \frac{1}{\lambda} \|x - y\|_*$
for any $x,y \in V^*$.

@@

%\label{section:generic-ftrl}

\begin{algorithm}[t]
\caption{\textsc{FTRL with Varying Regularizer}}
\label{algorithm:ftrl-varying-regularizer}
\begin{algorithmic}[1]
\REQUIRE Sequence of regularizers $\{R_t\}_{t=1}^\infty$
\STATE Initialize $L_0 \leftarrow 0$
\FOR{$t=1,2,3,\dots$}
\STATE $w_t \leftarrow \argmin_{w \in K} \left( \langle L_{t-1}, w \rangle + R_t(w) \right)$
\STATE Predict $w_t$
\STATE Observe $\ell_t \in V^*$
\STATE $L_t \leftarrow L_{t-1} + \ell_t$
\ENDFOR
\end{algorithmic}
\end{algorithm}

\textbf{Generic FTRL with Varying Regularizer.}
Our scale-free online learning algorithms are versions of the \textsc{Follow
The Regularized Leader} (FTRL) algorithm with varying regularizers, presented
as Algorithm~\ref{algorithm:ftrl-varying-regularizer}.  The following lemma
bounds its regret.

\begin{lemma}[Lemma 1 in \cite{Orabona-Crammer-Cesa-Bianchi-2014}]
\label{lemma:generic-regret-bound}
For any sequence $\{R_t\}_{t=1}^\infty$ of strongly convex lower
semi-continuous regularizers, regret of
Algorithm~\ref{algorithm:ftrl-varying-regularizer} is upper
bounded as
$$
\Regret_T(u) \le R_{T+1}(u) + R_1^*(0) + \sum_{t=1}^{T} \Breg_{R_t^*}(-L_t, -L_{t-1}) - R_t^*(-L_t) + R_{t+1}^*(-L_t) \; .
$$
\end{lemma}
%
The lemma allows data dependent regularizers. That is, $R_t$ can depend on the past loss
vectors $\ell_1, \ell_2, \dots, \ell_{t-1}$.

>>>>

\subsection{Convex Analysis}

The \emph{Bregman divergence} of a convex differentiable function $f$ is
defined as $\Breg_f(u,v) = f(u) - f(v) - \langle \grad f(v), u - v \rangle$.
Note that $\Breg_f(u,v) \ge 0$ for any $u,v$ which follows directly from the
definition of convexity of $f$.

The \emph{Fenchel conjugate} of a function $f:K \to \R$ is the function
$f^*:V^* \to \R \cup \{+\infty\}$ defined as $f^*(\ell) = \sup_{w \in K} \left(
\langle \ell, w \rangle - f(w) \right)$.  The Fenchel conjugate of any function
is convex (since it is a supremum of affine functions) and satisfies
 the \emph{Fenchel-Young inequality}
$$
\text{$\forall w \in K$, $\forall \ell \in V^*$} \qquad
f(w) + f^*(\ell) \ge \langle \ell, w \rangle \; .
$$

@@

\begin{proposition}[Fenchel Conjugates of Strongly Convex Functions]
\label{proposition:conjugate-properties}
Let $K \subseteq V$ be a non-empty closed convex set with diameter $D:=\sup_{u,v \in K} \|u-v\|$.
Let $\lambda > 0$, and let $f:K \to \R$ be a lower semi-continuous function
that is $\lambda$-strongly convex with respect to $\|\cdot\|$.
The Fenchel conjugate of $f$ satisfies:
\begin{enumerate}

\item $f^*$ is finite everywhere and differentiable.

\item For any $\ell \in V^*$, $\grad f^*(\ell) = \argmin_{w \in K} \left( f(w) - \langle \ell, w \rangle \right)$

\item For any $\ell \in V^*$, $f^*(\ell) + f(\grad f^*(\ell)) = \langle \ell, \grad f^*(\ell) \rangle$.

\item $f^*$ is $\frac{1}{\lambda}$-strongly smooth i.e. for any $x,y \in V^*$, $\Breg_{f^*}(x, y) \le \frac{1}{2\lambda} \|x - y\|_*^2$.

\item $f^*$ has $\frac{1}{\lambda}$-Lipschitz continuous gradients i.e.
for any $x,y \in V^*$,
$\|\grad f^*(x) - \grad f^*(y)\| \le \frac{1}{\lambda} \|x - y\|_*$.

@@

\begin{algorithm}[t]
\caption{\textsc{FTRL with Varying Regularizer}}
\label{algorithm:ftrl-varying-regularizer}
\begin{algorithmic}[1]
\STATE Initialize $L_0 \leftarrow 0$
\FOR{$t=1,2,3,\dots$}
\STATE Choose a regularizer $R_t:K \to \R$
\STATE $w_t \leftarrow \argmin_{w \in K} \left( \langle L_{t-1}, w \rangle + R_t(w) \right)$
\STATE Predict $w_t$
\STATE Observe $\ell_t \in V^*$
\STATE $L_t \leftarrow L_{t-1} + \ell_t$
\ENDFOR
\end{algorithmic}
\end{algorithm}

\subsection{Generic FTRL with Varying Regularizer}
\label{section:generic-ftrl}

Our scale-free online learning algorithms are versions of the \textsc{Follow
The Regularized Leader} (FTRL) algorithm with varying regularizers, presented
as Algorithm~\ref{algorithm:ftrl-varying-regularizer}.  The following lemma
bounds its regret.

\begin{lemma}[Lemma 1 in \cite{Orabona-Crammer-Cesa-Bianchi-2014}]
\label{lemma:generic-regret-bound}
For any sequence $\{R_t\}_{t=1}^\infty$ of strongly convex lower
semi-continuous regularizers, regret of
Algorithm~\ref{algorithm:ftrl-varying-regularizer} is upper
bounded as
$$
\Regret_T(u) \le R_{T+1}(u) + R_1^*(0) + \sum_{t=1}^{T} \Breg_{R_t^*}(-L_t, -L_{t-1}) - R_t^*(-L_t) + R_{t+1}^*(-L_t) \; .
$$
\end{lemma}

\begin{proof}

\end{proof}
